Teaching a Class to Grade Itself using Game Theory

### 2013-09-08 Primes Write up.tex
Resolved merge conflicts

\section{Materials and Methods}
The goal of this research is to find a peer grading system that is as accurate and as efficient as possible. First, the problem must be defined in mathematical terms.

To begin with, a set of assumptions is created. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a mechanism. The same set of assumptions can be used for multiple mechanisms, which will allow us to evaluate different mechanisms side by side. To begin with, a simple set of assumptions was created:
\begin{enumerate}
  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$, $W$ is number of work units used
  \item Everyone is risk neutral with respect to happiness
  \item Students want good grades
\end{enumerate}

These assumptions, in layman's terms, state that student's are happiest when they do no work, want to be happy, want good grades, and have a function that expresses there happiness. Also, they state that students will not avoid nor specifically try and take risks to get happier.

\subsection{Benchmark}
Once the assumptions are complete, a benchmark can be selected based on the goals of the system. A benchmark will allow for a quantitative way to compare mechanisms. To define such a benchmark, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are. Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done. As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism. Mathematically, the goal is to minimize the maximum amount of work done by a single person, as well as minimize maximum deviation between any student's given grade and the grade their assignment deserves.

@@

\subsection{Rules}
After a simple set of assumptions and a benchmark are created, the assumptions need to be further developed into a true model that will become the ``rules'' of the game. To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes. This added complexity to the previously simple assumptions:
\begin{enumerate}
  \item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
  \item Everyone is risk neutral with respect to happiness
  \item Students want good grades
\end{enumerate}
into:
\begin{enumerate}
\item The objective score of an assignment is from 0 to 100
\item The objective score assigned by the professor is the correct objective score
\item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort
\item Not everyone has the ability to get the correct objective score
\item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
\item Students want good grades
\item People don't like doing work
\item Students are selfish and don't care about their friends
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Everyone is risk neutral with respect to happiness
\item All students can communicate with all other students
\end{enumerate}

@@

The next step in creating a mechanism
\section{The Problem}
In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100. All of these assignments must be graded by someone, and no one can grade their own assignment. Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.

[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload? Why do you care about accurate grades? If you just care about workload, give everyone 100. If you just care about grades, have the professor grade everything. Need to consider both to properly model the problem.]
Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested. This is where mechanism design and game theory comes into play. Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose. Then, game theory is used to mathematically predict student behavior to benchmark such a system. Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months. The end result is fairly complete, although there are still questions to be answered in future work.

>>>>

\section{Materials and Methods}
To create the models that are used to predict the behavior of the students, a set process was used each time. To begin with, a set of assumptions is created. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
%Note: Specify that the model refers to a single grading round: There are $n$ students and 1 professor. Every student comes to us with an ungraded paper (input) define the objective score o_i, we then give those papers grades(output) After a mechanism runs each student receives a grade $g_i$ and after performing $w_i$ units of work. Define the professor as index 0.%
\begin{enumerate}
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}
%add simple list%

%Explanation of the choice of assumption
% - We need to talk about happiness because it provides a numerical way to compare different outcomes
% - Why don't we care about our friends

%First objective%
No student can deviate from the truthful strategy to improve his happiness. In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

\subsection{Benchmark}
%Efficiency objective%
The next step is to create a system that will allow multiple different models to be compared and evaluated side by side; in other words, a benchmark needs to be created. To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are. Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done. As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism. In mathematical terms we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.

@@

% We now have a well defined problem that we need to solve. Of course the set of assumptions might not be very realistic as we will so we

Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ``''rules'' of the game. To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes. This turned the list of assumptions from the 
simple into:
%Repeat above corrections%
\begin{enumerate}
\item The objective score of an assignment is from 0 to 100%setting%
\item The objective score assigned by the professor is the correct objective score%setting%
\item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort

\item Not everyone has the ability to get the correct objective score

\item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
\item Students want good grades
\item People don't like doing work
\item Students are selfish and don't care about their friends
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Everyone is risk neutral with respect to happiness

\item All students can communicate with all other students

\end{enumerate}

@@

\section{The Problem}
In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100. All of these assignments must be graded by someone, and no one can grade their own assignment. Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.

%[Note from Matt and Christos: Add some discussion about the benchmark: why do you care about workload? Why do you care about accurate grades? If you just care about workload, give everyone 100. If you just care about grades, have the professor grade everything. Need to consider both to properly model the problem.]
Once the rules and assumptions have been defined and the benchmark determined, different grading mechanisms can be created and tested. This is where mechanism design and game theory comes into play. Mechanism design is used to create a system that satisfies a set of constraints and achieves a certain purpose. Then, game theory is used to mathematically predict student behavior to benchmark such a system. Starting from the simplest and most obvious approaches, various mechanisms were created, tested, and refined upon in an iterative process that spanned several months. The end result is fairly complete, although there are still questions to be answered in future work.
